R for Clinical Study Reports and Submission

### 2022-07-12 preface.Rmd
Remove section numbering in preface
Update author email
update R package links

## Folder structure

@@

## In this book

@@

## Philosophy

We share the same philosophy described in
Section 1.1 of the [R Packages](https://r-pkgs.org/intro.html#intro-phil) book
and quote here.

@@

## Authors and contributors

@@

  Yilong Zhang <<yilong.zhang@merck.com>>, Nan Xiao, Keaven Anderson, Yalin Zhu

>>>>

## Folder structure {.unnumbered}

@@

## In this book {.unnumbered}

@@

## Philosophy {.unnumbered}

We share the same philosophy described in
Section 1.1 of the [R Packages](https://r-pkgs.org/Introduction.html#intro-phil) book
and quote here.

@@

## Authors and contributors {.unnumbered}

@@

  Yilong Zhang <<elong0527@gmail.com>>, Nan Xiao, Keaven Anderson, Yalin Zhu

### 2022-07-12 project-folder.Rmd
update R package links

For a clinical trial project, it is also important to provide proper documentation for those help functions.
We use `roxygen2` to document functions.
For example, the header below defines each variable in `fmt_est`.
More details can be found in [Chapter 10 of the R Packages book](https://r-pkgs.org/man.html).

@@

The `man/` folder is used to save documentation automatically generated by `roxygen2`.
A typical workflow is to add `roxygen2` documentation before each function in the `R/` folder.
Then `devtools::document()` is used to generate all the documentation files in the `man/` folder.
More details can be found in [Chapter 10 of the R Packages book](https://r-pkgs.org/man.html).

@@

- [`devtools`](https://devtools.r-lib.org/): make package development easier.
  + A good overview can be found in [Chapter 2 of the R Packages book](https://r-pkgs.org/whole-game.html).
  + `devtools::load_all()`: load all functions in `R/` folder and running environment.
  + `devtools::document()`: automatically create documentation using `roxygen2`.
  + `devtools::check()`: automatically perform compliance check as an R package.
  + `devtools::build_site()`: automatically run analysis scripts in batch and create a `pkgdown` website.
- [`usethis`](https://usethis.r-lib.org/): automates repetitive tasks that arise during project setup and development.
- [`testthat`](https://testthat.r-lib.org/): streamline testing code.
  + A discussion of using the `testthat` for an A&R project can be found in (@madhutest).
- [`pkgdown`](https://pkgdown.r-lib.org/): generate static HTML documentation website for an R package
  + It also allows you to run all analysis code in batch.

@@

For an R package, there are already criteria to ensure R package integrity.
More details can be found in [Chapter 19 of the R Packages book](https://r-pkgs.org/r-cmd-check.html).

>>>>

For a clinical trial project, it is also important to provide proper documentation for those help functions.
We use `roxygen2` to document functions.
For example, the header below defines each variable in `fmt_est`.
More details can be found in [Chapter 16 of the R Packages book](https://r-pkgs.org/man.html).

@@

The `man/` folder is used to save documentation automatically generated by `roxygen2`.
A typical workflow is to add `roxygen2` documentation before each function in the `R/` folder.
Then `devtools::document()` is used to generate all the documentation files in the `man/` folder.
More details can be found in [Chapter 16 of the R Packages book](https://r-pkgs.org/man.html).

@@

- [`devtools`](https://devtools.r-lib.org/): make package development easier.
  + A good overview can be found in [Chapter 2 of the R Packages book](https://r-pkgs.org/Whole-game.html).
  + `devtools::load_all()`: load all functions in `R/` folder and running environment.
  + `devtools::document()`: automatically create documentation using `roxygen2`.
  + `devtools::check()`: automatically perform compliance check as an R package.
  + `devtools::build_site()`: automatically run analysis scripts in batch and create a `pkgdown` website.
- [`usethis`](https://usethis.r-lib.org/): automates repetitive tasks that arise during project setup and development.
- [`testthat`](https://testthat.r-lib.org/): streamline testing code.
  + A discussion of using the `testthat` for an A&R project can be found in (@madhutest).
- [`pkgdown`](https://pkgdown.r-lib.org/): generate static HTML documentation website for an R package
  + It also allows you to run all analysis code in batch.

@@

For an R package, there are already criteria to ensure R package integrity.
More details can be found in [Chapter 20 of the R Packages book](https://r-pkgs.org/check.html).

### 2022-07-12 project-management.Rmd
update R package links

In an R package development, the validation or testing is completed under the `test/` folder.
The testthat R package can be used to streamline the validation process.
More details of the `testthat` package for R package validation can be found in [Chapter 12 of the R package book](https://r-pkgs.org/tests.html).

>>>>

In an R package development, the validation or testing is completed under the `test/` folder.
The testthat R package can be used to streamline the validation process.
More details of the `testthat` package for R package validation can be found in [Chapter 12 of the R package book](https://r-pkgs.org/testing-basics.html).
